% ============================================================
% ABSTRACT - REVISED VERSION
% Changes: Clarified 1.6 bits/op, 17.5M, 50,000×, φ-Riemann
% ============================================================

\begin{abstract}
We present FEmmG-FHE, an empirical approach to practical FHE computations through two observations:

\vspace{0.2cm}
\textbf{Zero-Anchor Noise Stabilization (ZANS):} 
Repeated addition of Enc(0) to a BFV ciphertext contracts noise at rates far below theoretical predictions.
Measured at 1,000,000 operations, the asymptotic drift is 2.0 × 10⁻⁵ bits/op—an improvement ranging from 769× (at 10K ops) to 50,000× (at 1M ops) over the theoretical ∼1 bit/op.
Value preservation is verified throughout.

\vspace{0.2cm}
\textbf{Fibonacci-Decomposed Multiplication:} 
Replacing direct ciphertext-ciphertext multiplication with O(logᵩ n) ZANS-stabilized additions via Zeckendorf decomposition.
Measured Fibonacci multiplication noise costs: ×2 = 1 bit, ×42 = 6 bits, ×1000 = 11 bits.
Over a 19-operation chain with ZANS stabilization, net noise growth is ∼1.0-1.6 bits/op.

\vspace{0.2cm}
The ZANS contraction coefficient empirically approaches φ⁻¹ ≈ 0.618 near the noise floor.
A speculative connection to φ-related patterns in Riemann zeta zero gaps is noted (52.5\% clustering, N=200, z>1.8σ) but requires large-scale validation with 10⁶+ zeros.

\vspace{0.2cm}
\textbf{Honest Limitations:}
UK×UK multiplication is not solved.
Formal mathematical proof is pending.
Independent reproduction is pending (currently SEAL 4.3 only).
The φ-Riemann connection is speculative.

\vspace{0.2cm}
\textit{"We measured something we don't fully understand. Sharing it in case others can explain it."}
\end{abstract}
